---
title: "HW4"
author: "RogerZhang"
date: "2018/2/24"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Plot Forest fire with Wind strength on Y axis, different week days on x axis.
```{r}
library(ggplot2)
library(base)
ggplot(data=forestfires, mapping=aes(x=day, fill=factor(forestfires$wind)))+
  geom_bar()
```
## We may conclude that wind is not a factor with respect to which day the forest fire is occuring.


## Forestfire boxplot
```{r}
library(ggplot2)
library(base)

ggplot(data=forestfires, mapping=aes(group=day, x=day, y=temp))+
  geom_boxplot()
```
## Boxplots tell us the range of temperature forest fires occured in. Again, separated by day, not dates. Dates are a bit hard to be used as they have letters for 12 months.


## Forest fire month vs RH values
```{r}
library(ggplot2)
library(base)
ggplot(data=forestfires, mapping=aes(group=month, x=month, y=RH))+
  geom_violin()
```
## We can see a range of RH values correspond to different months. However, no such value exist for November and January.